\section*{Acknowledgement}
Throughout the project period my classmates has been at great help to discuss and generate ideas.

Especially thanks to the people listed below.
\begin{itemize}
	\item My supervisor Kjeld Jensen for giving solutions and help when needed.
	\item Developer of MarkerLocator Henrik Midtiby for helping me understand and adding functionality to his software.
	\item Friend Morten Albeck Nielsen for meeting once a week to help generating ideas, debugging, sparring and proof reading the thesis.
	\item Friends Mads Tilgaard Jensen, Eskild Andresen \& Michael René Andersen for listening to technical issues, evaluating solutions and carrying out tests.
	\item My girlfriend Anna Riisberg Soerensen for proofreading the thesis and understanding the time required throughout this project period.
\end{itemize}


\textbf{AutoQuad} is the flight controller used in this project. The Author was among the first students using AutoQuad on SDU, but the first student to make changes to the firmware and to communicate with AQ using CAN-bus. The AutoQuad firmware is not documented at all, so much time was spend reading through code and trying to figure out how it works. A great amount of time was also spend on more practical things like getting to know their Development Environment (CrossWorks for ARM)\footnote{http://www.rowley.co.uk/arm/} in order to compile their firmware, waiting for Quatos\footnote{The controller, Quatos,  used in AutoQuad is not Open Source so a license had to be bought by SDU} license and getting familiar with the flashing process of AutoQuad.\\
Much of the gained knowledge about AutoQuad and how to do debugging has been written down to share with other students. It can be found on the USB-key handed in \textit{Appendix/SDU-UASAutoQuaddocumentation.pdf and SDU-UASAutoQuadsourcecodedocumentation.pdf}. Text marked with green is written by the author.